Research log

### 2023-01-28 docs/preregisteredMethodsAndResults.Rmd
typo

Participants were not significantly above chance in judging which of the two presented games came from a pretender (`r apa_print(t.test(E4.judge_summary_df$accuracy, mu=0.5))$full_result`). This was the case also when focusing on words that judges encountered when pretending (`r apa_print(t.test(E4.judge_summary_df$accuracy_pretend_words, mu=0.5))$full_result`), and when focusing on words that judges encountered when playing normally (`r apa_print(t.test(E4.judge_summary_df$accuracy_nonpretend_words, mu=0.5))$full_result`).

>>>>

Participants were not significantly above chance in judging whether the presented game came from a pretender (`r apa_print(t.test(E4.judge_summary_df$accuracy, mu=0.5))$full_result`). This was the case also when focusing on words that judges encountered when pretending (`r apa_print(t.test(E4.judge_summary_df$accuracy_pretend_words, mu=0.5))$full_result`), and when focusing on words that judges encountered when playing normally (`r apa_print(t.test(E4.judge_summary_df$accuracy_nonpretend_words, mu=0.5))$full_result`).
